\documentclass{tropical}
\title{Tropical.cls}
\author{Nyan}
\date{Last updated \today}
\begin{document}
\maketitle\outline[Outline called by \fakecmd{outline}.]
\section{A section}
\begin{frame}{A frame title :0}
A demonstration of the appearance (and minor added features) of \texttt{tropical.cls}, a Beamer style by the mentioned author.
\begin{block}{Block}
Call by the usual \fakecmd{begin\{block\}}\dots\fakecmd{end\{block\}} environment, this block's the same color as the main theme.
\end{block}
\begin{warn}[Alertblock]
For alertblocks and exampleblocks, names have been shortened; their new appellations are the environments \texttt{warn} and \texttt{exmp}. 
\end{warn}
\end{frame}
\section{More things}
\subsection{A subsection}
\begin{frame}{Other addendums}
No font change because it doesn't make any typographical sense. Plus, I'm too lazy to.
\begin{exmp}[Exampleblock]
As mentioned earlier this block's name has been shortened to \texttt{exmp}.
\end{exmp}
\claim[just in case!]{Might need this during solutions to certain problems? On the other hand, for others, this might just be a write-up mechanic isomorphic to the so-called `extremal principle' in combina-torics.}
\end{frame}
\begin{frame}{Comments}
\begin{block}{Remark}
The theme used (out of all Beamer defaults) is the middest one, Warsaw.
\\
Well, why did I choose it? I guess I liked the boxes having shadows, and the footer not being very corpulent?
\end{block}
{\itshape ``Warsaw LMFAO'' -- dennisc}
\\[4pt]
Next thing to do: integrate this \texttt{.cls} with Dennis's \texttt{.beam} invention?
\end{frame}
\begin{frame}{Other blocks?}
\begin{warn}[Alertblock for comparison]
Ok.
\end{warn}
\begin{thm}[Thmblock by me]
For some reason, I wanted to create a fourth block, so instead of being smart and using some variant of \fakecmd{let}, I `mocked' the block code using \texttt{tcolorbox}.\\
This block's called \texttt{thmblock}, or \texttt{thm} for short also works.\\
Last thing to do, make the \texttt{colframe} a gradient...
\end{thm}
\begin{block}{Block for comparison}
Not cosmetically perfect, but ehh, close enough!
\end{block}
I also just noticed that the alertblock is actually a bit smaller than the regular block :P
\end{frame}
\end{document}
